% !TEX root = ../main.tex

\section*{3}
\subsection*{(a)}
Our rectangle is a region of $2 \delta \times \delta$. \\

Because $\delta$ is the smallest diameter among all three-disks, then the maximum distance among any three points must be at least some constant factor of $\delta$. (Indeed, if the three points create an equilateral triangle, then the distance is 
$\frac{\sqrt(3) \cdot \delta} {2}$. If the third point is very close to the line created from the first 2 points, then the maximum distance is $\delta$).\\

Now we try to put as many points as possible into the rectangle region, following the rule: there are no three-disks with diameters less than $\delta$. It is obvious that we have to put the points at a smallest possible distance to each other. \\

To maximize the number of the points, we will put the first point $P_1$ in the center of the left border of the rectangle. Then we can insert the next point $P_2$ at a very close position to $P_1$ (much smaller than $\delta$). Then the next point $P_3$ must be at least at a distance of $\delta$ from either $P_1$ or $P_2$. There is also the other case when we put $P_2, P_3$ in which $P_1P_2P_3$ forms an equilateral triangle, and the distance of the edges is $\frac{\sqrt(3) \cdot \delta} {2}$. If we put any other point, there will be 3 points that create a smaller disk. \\

Similarly, we do the same thing for the other half of the rectangle, however we have to take care of the situation when there are 3 points close to the center of the rectangle which can form a smaller three-disk. \\

Therefore, the number of points in the rectangle is bounded by a constant.

\subsection*{(b)}

\begin{algorithm}[h]
  \caption{PaneSweepThree-Disk}
  \label{alg:panesweep}
  \begin{algorithmic}
      \Require set of points $P$
      \State Initialize $Q$ an event queue and $S$ a status data structure storing $p_{i.x}$ and $\delta \leftarrow 0$
      \State Sort $P$ in $y$ value in descending order and put it into $Q$
      \State Construct the first three-disk from $p_1, p_2$ and $p_3$ and update $\delta$
      \For{  $p_i \in P$ where $3 < i < n$}
	\State Remove $p_j$ from $S$ where  $ p_{j.y} > \delta + p_{i.y} $
	\State Add $p_{i.x}$ to $S$
	\State Find $R$, a set of points whose $x$ value is in the range  $[ p_{i.x} - \delta,  p_{i.x} + \delta ]$ from $S$
	\If{ $|R| > 1$ }
	\State Find a smaller three-disk by trying all combination of $R \cup \{p_i\}$ and update $\delta$
	\EndIf
      \EndFor
      \State report $\delta$
\end{algorithmic}
\end{algorithm}

In this algorithm, we use array for $Q$ and a Binary Search Tree for $S$.  \\

The algorithm returns the correct solution. If there is a smaller three-disk in the set of points, it should be covered when the 
sweep line scans through the lowest point among the three, and $\delta$ will be updated.\\

Instead of comparing every combination, it scans from the top point to the bottom point and update the smallest three-disk at each step. At each step, the number of combinations needed to find a new diameter is a constant because the numbers of points inside the rectangle of size $2 \delta \times \delta$ is bounded by a constant, as being proven in part (a). \\

The cost of sorting the events is $O(n\log n)$. \\

For each of the event point, each removal from the S takes constant time, the insertion also takes $O(\log n)$ time, the extraction of the values inside the rectangle depends on the number of items inside that range - which is bounded by a constant as being proven above. \\

So in the normal case, the algorithm runs in $O(n \log n)$ time. \\

The degenerate case is when most of the points ($O(n)$) are inside the range $\delta$, then the removal is costly. In such a case, it takes $O(n)$ to remove every item above the range of $\delta$. Then the algorithm runs in $O(n^2)$ time.\\
